### 2023-08-10 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
working on figures

\begin{figure*}[t]
%\begin{figure}
  \centering
  \subfigimg[width=0.48\linewidth]{(a)}{figures/SC_top.pdf}
  \subfigimg[width=0.48\linewidth]{(b)}{figures/SC_bot.pdf}
  \subfigimg[width=0.48\linewidth]{(c)}{figures/SCp55_top.pdf}
  \subfigimg[width=0.48\linewidth]{(d)}{figures/SCp55_bot.pdf}
  \subfigimg[width=0.48\linewidth]{(e)}{figures/MCp5_top.pdf}
  \subfigimg[width=0.48\linewidth]{(f)}{figures/MCp5_bot.pdf}
  \caption{\label{fig:BLvelocities} The co-moving velocity field in the
  thin fluid layer between vesicles and the stenosis geometry. The
  vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
  single-component with $b(u) = 0.55$; (e/f): multicomponent. The top
  layers are in (a/c/e) and the bottom layers are in (b/d/f). The
  profiles are ploted at slices where the pressure gradient transitions
  from a value that is negative, zero, positive, zero, and negative. The
  right plots show the tangential stress with the five slices denoted by
  the marks. Note that the reversal in the pressure gradient occurs when
  the tangential stress is sufficiently large, in magnitude.}
%\end{figure}
\end{figure*}

@@

\begin{figure}[h]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
  $Ca = 0.25$. The lipid distribution is initialized to already be phase
  separated in the top and bottom rows, and the middle row has a random
  initial lipid distribution. The preferred lipid distribution has the
  stiff region passing through the contraction before the floppy
  region.}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MC_variableConc.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
  \caption{\label{fig:RA5} \small A vesicle passing through a
  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
  the Capillary number is $Ca = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=b_{\max}$; (b) multicomponent
  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
  (d) multicomponent with 35\% floppy region; (e) multicomponent with
  45\% floppy region. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions.}
\end{figure}

\begin{table}[h]
  \centering
  \begin{tabular}{l|ccccc}
    \hline
    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% \\ 
    Time  & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:contractingTimes} The time required for the
  vesicles to completely pass through the neck.}
\end{table}
%\begin{table}[H]
%  \centering
%  \begin{tabular}{l|c}
%    Floppy percentage & Time to pass through neck \\
%    \hline
%    0\% &  2.32 \\
%    15\% & 2.30 \\
%    25\% & 2.29 \\
%    35\% & 2.26 \\
%    45\% & 2.24 \\
%%    Single-component &  2.32 \\ %2.3173\\
%%    15\% Multicomponent & 2.30 \\%2.2960\\
%%    25\% Multicomponent & 2.29 \\%2.2868\\
%%    35\% Multicomponent & 2.26 \\%2.2637\\
%%    45\% Multicomponent & 2.24 \\%2.2388\\
%    \hline
%  \end{tabular}
%  \caption{\label{tbl:contractingTimes} The time required for the
%  vesicles to completely pass through the neck.}
%\end{table}

@@

\begin{figure}[h]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
  \subfigimg[width=\columnwidth]{(a)}{figures/ContractingEnergy_SC.pdf}
  \subfigimg[width=\columnwidth]{(b)}{figures/ContractingEnergy_MC.pdf}
%  \subfigimg[width=\columnwidth]{(a)}{figures/bendingSC.pdf}
%  \subfigimg[width=\columnwidth]{(b)}{figures/bendingEngMC45.pdf}
  \caption{\label{fig:bendingSC_contracting} The bending energy of (a) a
  single-component vesicle, and (b) a multicomponent vesicle whose
  boundary is 45\% floppy passing through a contracting geometry. The
  vesicle shape at different locations are included. We can clearly see
  that the sudden increases and decreases in the bending energy are due
  to transitions between lower energy and higher energy shapes.}
\end{figure}

>>>>

\begin{figure*}[t]
%\begin{figure}
  \centering
  \subfigimg[width=0.48\linewidth]{(a)}{figures/SC_top.pdf}
  \subfigimg[width=0.48\linewidth]{(b)}{figures/SC_bot.pdf}
  \subfigimg[width=0.48\linewidth]{(c)}{figures/SCp55_top.pdf}
  \subfigimg[width=0.48\linewidth]{(d)}{figures/SCp55_bot.pdf}
  \subfigimg[width=0.48\linewidth]{(e)}{figures/MCp5_top.pdf}
  \subfigimg[width=0.48\linewidth]{(f)}{figures/MCp5_bot.pdf}
  \caption{\label{fig:BLvelocities} \small The co-moving velocity field
  in the thin fluid layer between vesicles and the stenosis geometry.
  The vesicles are (a/b): single-component with $b(u) = 1$; (c/d):
  single-component with $b(u) = 0.55$; (e/f): multicomponent. The top
  layers are in (a/c/e) and the bottom layers are in (b/d/f). The
  profiles are ploted at slices where the pressure gradient transitions
  from a value that is negative, zero, positive, zero, and negative. The
  right plots show the tangential stress with the five slices denoted by
  the marks. Note that the reversal in the pressure gradient occurs when
  the tangential stress is sufficiently large, in magnitude.}
%\end{figure}
\end{figure*}

@@

\begin{figure}[h]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(a)}{figures/rightSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(b)}{figures/randSep.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 2cm .5cm},clip]{(c)}{figures/leftSep.pdf}
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MCp5.pdf}
  \caption{\label{fig:RA6leftRightRand} \small A multicomponent vesicle
  with 50\% floppy region passing through a contracting geometry. The
  vesicle's reduced area is $\alpha = 0.6$ and the capillary number is
  $Ca = 0.25$. The lipid distribution is initialized to be (a) phase
  separated with the floppy region leading; (b) random; (c) phase
  separated with the stiff region leading.}
\end{figure}

@@

%\begin{figure*}[t]
\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MC_variableConc.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
  \caption{\label{fig:RA5} \small A vesicle passing through a
  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
  the Capillary number is $Ca = 0.25$. The vesicles are: (a)
  single-component with bending modulus $b=b_{\max}$; (b) multicomponent
  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
  (d) multicomponent with 35\% floppy region; (e) multicomponent with
  45\% floppy region. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions.}
\end{figure}
%\end{figure*}

\begin{table}[h]
  \centering
  \begin{tabular}{l|ccccc}
    \hline
    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% \\ 
    Time  & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:contractingTimes} \small The time required for the
  vesicles to completely pass through the neck.}
\end{table}
%\begin{table}[H]
%  \centering
%  \begin{tabular}{l|c}
%    Floppy percentage & Time to pass through neck \\
%    \hline
%    0\% &  2.32 \\
%    15\% & 2.30 \\
%    25\% & 2.29 \\
%    35\% & 2.26 \\
%    45\% & 2.24 \\
%%    Single-component &  2.32 \\ %2.3173\\
%%    15\% Multicomponent & 2.30 \\%2.2960\\
%%    25\% Multicomponent & 2.29 \\%2.2868\\
%%    35\% Multicomponent & 2.26 \\%2.2637\\
%%    45\% Multicomponent & 2.24 \\%2.2388\\
%    \hline
%  \end{tabular}
%  \caption{\label{tbl:contractingTimes} The time required for the
%  vesicles to completely pass through the neck.}
%\end{table}

@@

\begin{figure}[h]
  \centering
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
  \subfigimg[width=\columnwidth]{(a)}{figures/ContractingEnergy_SC.pdf}
  \subfigimg[width=\columnwidth]{(b)}{figures/ContractingEnergy_MC.pdf}
%  \subfigimg[width=\columnwidth]{(a)}{figures/bendingSC.pdf}
%  \subfigimg[width=\columnwidth]{(b)}{figures/bendingEngMC45.pdf}
  \caption{\label{fig:bendingSC_contracting} \small The bending energy
  of (a) a single-component vesicle, and (b) a multicomponent vesicle
  whose boundary is 45\% floppy passing through a contracting geometry.
  The vesicle shape at different locations are included. We can clearly
  see that the sudden increases and decreases in the bending energy are
  due to transitions between lower energy and higher energy shapes.}
\end{figure}
